Download data

### 2024-02-28 scripts/subsetDataforCrews.Rmd
fn to writee out results to tabular

blm_surf <- st_read(paste0(p, 'Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp'), quiet = TRUE)
usfs_surf <- st_read(paste0(p, 'Public_land_ownership/USFS_West_simplified/USFS_West_simplified.shp'), quiet = TRUE)
invasives <- rast(paste0(p, 'MRLC/', '2023_InvGrassCover.tif'))
change_intensity <- rast(paste0(p, 'MRLC/total_change_intensity_index/', 'TCII_3arc.tif'))
fire_perimeters <- st_read( quiet = T,
  paste0(p, 'NIFC_perimeters/', 'InterAgencyFirePerimeterHistory_All_Years_View-Simplified.shp'))
SWSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'desertSW/desert_southwest_provisional_seed_transfer_zones_USGS.shp')) %>% 
  select(seed_zone = Zone) %>% 
  mutate(Dataset = 'SWSTZ', .before = geometry, seed_zone = as.character(seed_zone))
BOWERSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'WWETAC_STZ/GB_2013_revised_reduced.shp')) %>% 
  select(seed_zone) %>% 
  mutate(Dataset = 'BowerRevised', .before = geometry)
STZ <- bind_rows(BOWERSTZ, SWSTZ) %>% 
  st_transform(5070)
roads <- st_read(quiet = T, paste0(p, 'blmRoadsSOS24/processed/BLM_roads.shp'))
admin_boundaries <- st_read(paste0(p, 'Public_land_ownership/BLM_ADMU/BLM_ADMU_BOUNDARIES.shp'), quiet = TRUE)
allotments <- st_read(
  file.path(p, 'Public_land_ownership/BLM_Natl_Grazing_Allotment_Polygons/Allotment-simp.shp')) %>% 
  select(ALLOT_NAME)

@@

@@

>>>>

blm_surf <- st_read(paste0(p, 'Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp'), quiet = TRUE)
usfs_surf <- st_read(paste0(p, 'Public_land_ownership/USFS_West_simplified/USFS_West_simplified.shp'), quiet = TRUE)
invasives <- rast(paste0(p, 'MRLC/', '2023_InvGrassCover.tif'))
change_intensity <- rast(paste0(p, 'MRLC/total_change_intensity_index/', 'TCII_3arc.tif'))
fire_perimeters <- st_read( quiet = T,
  paste0(p, 'NIFC_perimeters/', 'InterAgencyFirePerimeterHistory_All_Years_View-Simplified.shp'))
SWSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'desertSW/desert_southwest_provisional_seed_transfer_zones_USGS.shp')) %>% 
  select(seed_zone = Zone) %>% 
  mutate(Dataset = 'SWSTZ', .before = geometry, seed_zone = as.character(seed_zone))
BOWERSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'WWETAC_STZ/GB_2013_revised_reduced.shp')) %>% 
  select(seed_zone) %>% 
  mutate(Dataset = 'BowerRevised', .before = geometry)
STZ <- bind_rows(BOWERSTZ, SWSTZ) %>% 
  st_transform(5070)
roads <- st_read(quiet = T, paste0(p, 'blmRoadsSOS24/processed/BLM_roads.shp'))
admin_boundaries <- st_read(paste0(p, 'Public_land_ownership/BLM_ADMU/BLM_ADMU_BOUNDARIES.shp'), quiet = TRUE)
allotments <- st_read(
  file.path(p, 'Public_land_ownership/BLM_Natl_Grazing_Allotment_Polygons/Allotment-simp.shp'), quiet = T) %>% 
  select(ALLOT_NAME)

@@

```{r generate projects for crews}

@@

Now we can generate estimates of flowering duration in certain field offices

```{r generate phenology spreadsheet for crews}

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
lapply(X = teams_list[1], 
       FUN = phen_tabulator,
       path = p2ts, 
       admu = admin_boundaries, 
       target_species = spp_needed
       )

focal_area <- dplyr::filter(admin_boundaries, ADMU_NA == str_to_upper('St. George Field Office' )) |>
  sf::st_union() |>
  sf::st_transform(5070) |>
  vect()

focal_r <- rast(file.path(path, f[[1]]))
out_v <- terra::extract(focal_r, focal_area, method = 'simple', fun = table, na.rm = T, ID = FALSE)
pos <- unlist(lapply(out_v, function(x){x1 <- colnames(x)[which.max(x)]})) # most common doy for event

#names(out_v) <- c('Initation', 'Peak', 'Cessation')
```
